---
title: "PCERP Project Site"
output: flexdashboard::flex_dashboard
self_contained: false
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, warning=FALSE}
source("libraries.R")
source("project_recipients.R")
source("project_indicators.R")
source("leaflet_maps.R")
```

# Project Description

The Philippines COVID-19 Emergency Response Project (PCERP), with the
Project Development Objective (PDO) to strengthen the Philippines'
capacity to prevent, detect, and respond to the threat posed by COVID-19
and strengthen national systems for public health preparedness, was
approved by the World Bank on 22 April 2020.

Despite recent progress, the Philippines remains one of the countries
most affected by the COVID-19 in East Asia and Pacific, rendering
vaccine purchase and deployment a national priority. With the
availability of vaccines, the Philippines has now an opportunity to add
a significant new layer to its COVID-19 emergency response. Procuring
and administering vaccines is critical to reducing mortality from COVID,
opening the economy in earnest and arresting the decline in GDP,
employment and incomes. Hence, Additional Financing (AF) was sought by
the country to enable affordable and equitable access to COVID-19
vaccines and help ensure effective vaccine deployment in the country
through an enhanced vaccination system and to further strengthen
preparedness and response activities.

The original approved loan financing of US\$ 100 Million (Loan no.
9105-PH) had been increased by US\$ 500 Million through the Additional
Financing in 19 March 2021, to cover the procurement of vaccines against
COVID- 19 and to support the DOH National Deployment and Vaccination
Plan (NDVP) (Loan no. 9220-PH). The new total of the Project financing
is US\$ 600 Million.

The expected project beneficiaries will be the general population,
including infected people, at-risk populations, particularly the elderly
and people with chronic conditions, medical and emergency personnel,
medical and testing facilities, and public health agencies engaged in
the response.

The project is comprised of the following four components:

Component 1: Strengthening Emergency COVID-19 Health Care Response (US\$
577,117,000) with the following sub-component:<br>          1.1
Provision of medical and laboratory equipment and reagents;<br>         
1.2 Provision of medical supplies, including Personal Protective
Equipment (PPE), medical countermeasures, COVID-19 vaccines, medicines,
and ambulances;<br>          1.3 Regular and intensive care isolation
rooms with negative pressure;<br>          1.4 Deployment of COVID-19
vaccines (new sub-component, financed by counterpart funding from the
GOP

Component 2: Strengthening laboratory capacity at national and
sub-national level to support Emerging Infectious Diseases (EIDs)
Prevention, Preparedness, and Response (US\$ 15,678,000): It includes
improving, retrofitting, and refurbishing one national reference
laboratory--the Research Institute for Tropical Medicine (RITM)---as
well as six sub-national and public health laboratories in Baguio, Cebu,
Davao, Surigao City, and Manila;

Component 3: Implementation Management and Monitoring and Evaluation
(US\$ 7,205,000): This component supports project management and
monitoring, including the creation of a project management team and
development of project monitoring and evaluation system; and

Component 4: Contingent Emergency Response Component (CERC) (US\$0),
which supports immediate response to an eligible crisis or health
emergency.

The Project Operations Manual (DOH Department Circular no. 2021-0142),
Project's Implementation Arrangements (DOH Department Order no.
2021-0205), Guidelines on the Project's Civil Works Implementation (DOH
Department Circular no. 2020-0398), and the PCERP Contingency Emergency
Response Component -- Emergency Response Operations Manual [CERC--EROM]
(DOH Department Circular no. 2021-0314) are available in the resources
tab.

The closing date of the Project is on December 29, 2023.


# Project Recipients

## Mapping {.tabset}
### Civil Works

```{r}
plotted_GIS
```

## Recipient Tables {.tabset}
### Mechanical Ventilator
```{r}
recipients_equipment%>%
  filter(project_description %in% c("Mechanical Ventilator")
         )%>%
  select(facility_name,
         region,
         project_description,
         quantity)%>%
  arrange(project_description)%>%
  mutate(facility_name = facility_name%>%
           str_replace_all(".*General Hospital and Satellite Trauma Center",
                           "Las Piñas General Hospital and Satellite Trauma Center"))%>%
  DT::datatable(
    colnames = c("Item" = "project_description",
                 "Region" = "region",
                 "Facility Name" = "facility_name",
                 "Quantity" = "quantity"),
    height = 850,
    filter = "none",
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 2:4
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```

### Portable X-ray
```{r}
recipients_equipment%>%
  filter(project_description %in% c("Portable X-ray")
         )%>%
  select(facility_name,
         region,
         project_description,
         quantity)%>%
  arrange(project_description)%>%
  mutate(facility_name = facility_name%>%
           str_replace_all(".*General Hospital and Satellite Trauma Center",
                           "Las Piñas General Hospital and Satellite Trauma Center"))%>%
  DT::datatable(
    colnames = c("Item" = "project_description",
                 "Region" = "region",
                 "Facility Name" = "facility_name",
                 "Quantity" = "quantity"),
    height = 850,
    filter = "none",
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 2:4
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```

### Infusion Pump
```{r}
recipients_equipment%>%
  filter(project_description %in% c("Infusion Pump")
         )%>%
  select(facility_name,
         region,
         project_description,
         quantity)%>%
  arrange(project_description)%>%
  mutate(facility_name = facility_name%>%
           str_replace_all(".*General Hospital and Satellite Trauma Center",
                           "Las Piñas General Hospital and Satellite Trauma Center"))%>%
  DT::datatable(
    colnames = c("Item" = "project_description",
                 "Region" = "region",
                 "Facility Name" = "facility_name",
                 "Quantity" = "quantity"),
    height = 850,
    filter = "none",
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 2:4
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```

### Ambulance
```{r}
recipients_equipment%>%
  filter(grepl("Ambulance", .$project_description, ignore.case = T)
         )%>%
  select(facility_name,
         region,
         project_description,
         quantity)%>%
  arrange(project_description)%>%
  mutate(facility_name = facility_name%>%
           str_replace_all(".*General Hospital and Satellite Trauma Center",
                           "Las Piñas General Hospital and Satellite Trauma Center"))%>%
  DT::datatable(
    colnames = c("Item" = "project_description",
                 "Region" = "region",
                 "Facility Name" = "facility_name",
                 "Quantity" = "quantity"),
    height = 850,
    filter = "none",
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 2:4
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```

### Consumables
```{r}
recipients_equipment%>%
  filter(project_description %in% c("PPE and Mask")
         )%>%
  select(facility_name,
         region,
         project_description,
         quantity)%>%
  arrange(project_description)%>%
  mutate(facility_name = facility_name%>%
           str_replace_all(".*General Hospital and Satellite Trauma Center",
                           "Las Piñas General Hospital and Satellite Trauma Center"))%>%
  DT::datatable(
    colnames = c("Item" = "project_description",
                 "Region" = "region",
                 "Facility Name" = "facility_name",
                 "Quantity" = "quantity"),
    height = 850,
    filter = "none",
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 2:4
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```

### RT PCR
```{r}
rt_pcr%>%
  DT::datatable(
    colnames = c(
      "Province" = "province",
      "Region" = "region",
      "Facility Name" = "facility_name"
    ),
    height = 850,
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 1:2
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```

### Civil Works
```{r}
merged_GIS%>%
  select(Facility.Name,
         project_description,
         status)%>%
  arrange(project_description,
          Facility.Name)%>%
  mutate(Facility.Name = Facility.Name%>%
           str_replace_all(".*General Hospital and Satellite Trauma Center",
                           "Las Piñas General Hospital and Satellite Trauma Center"))%>%
  DT::datatable(
    colnames = c("Item" = "project_description",
                 "Status" = "status",
                 "Facility Name" = "Facility.Name"),
    height = 850,
    filter = "none",
    options = list(
      scrollY = "450px",
      columnDefs = list(
        list(
          className = 'dt-center',
          targets = 2:3
          )
        ),
      # searching = F,
      pageLength = 20
      )
    )

```


# Environmental and Social Framework (ESF)

The Environmental and Social Management Framework (ESMF):

-   is an instrument that examines risks and impacts of the project and
    its components which cannot be determined until the program or the
    subproject details have been identified

-   describes principles, processes and technical guidance to the
    Project implementing agencies and their consultants to assess the
    environmental and social (E&S) risks and impacts of the Project
    activities

-   developed in accordance with the World Bank's Environmental and
    Social Standards (ESSs)

The Environmental and Social Standards (ESS) include:

```{r}
tibble(
  col1 = paste0("ESS", 1:10),
  col2 = c(
    "Assessment and Management of Environmental and Social Risks and Impacts",
    "Labor and Working Conditions",
    "Resource Efficiency and Pollution Prevention and Management",
    "Community Health and Safety",
    "Land Acquisition, Restrictions on the Land Use and Involuntary Resettlement",
    "Biodiversity Conservation and Sustainable Management
of Living Natural Resources",
"Indigenous Peoples/Sub-Saharan African Historically Underserved Traditional Local Communities",
"Cultural Heritage",
"Financial Intermediaries",
"Stakeholder Engagement and Information Disclosure"
  )
)%>%
  kbl(col.names = NULL)%>%
  column_spec(1:2,
              border_left = T,
              border_right = T)%>%
  kable_styling("striped")
```

\~ESS 5,6,8,and 9 are not related to the Project.\~

The objectives of the ESMF are as follows:

-   assess potential E&S risks and impacts of the Project & propose
    mitigation measures for risks/impacts

-   establish clear procedures for the E&S screening, review, approval,
    and implementation of activities

-   specify appropriate roles and responsibilities, and outline the
    necessary reporting procedures

-   identify the training and capacity building needed to successfully
    implement the provisions of the ESMF

-   address mechanisms for public consultation and disclosure of project
    documents as well as redress of possible grievance f. establish the
    budget requirement for implementation of the ESMF

# Results Framework Indicators

### The Project's Results Framework Indicators for the Parent Project (Original Loan) and Additional Financing are as follows:

**A. Project Development Objective Indicators**

```{r}
PDI%>%
    kbl(booktabs = T, format = "html", align = "l")%>%kable_styling(full_width = T)

```
**B. Intermediate Results Indicators**

```{r}
IRI$`Strengthening Emergency COVID-19 Health Care Response`%>%
    kbl(booktabs = T, format = "html", align = "l", caption = "Strengthening Emergency COVID-19 Health Care Response")%>%kable_styling(full_width = T)
IRI$`Strengthening Laboratory Capacity at National and Sub-National Level`%>%
    kbl(booktabs = T, format = "html", align = "l", caption = "Strengthening Emergency COVID-19 Health Care Response")%>%kable_styling(full_width = T)
IRI$`Implementation Management and Monitoring and Evaluation`%>%
    kbl(booktabs = T, format = "html", align = "l", caption = "Strengthening Emergency COVID-19 Health Care Response")%>%kable_styling(full_width = T)

```


# Resources
<br>

[Project Operations Manual](https://doh.gov.ph/sites/default/files/basic-page/DC%20NO.%202021-0142%20UPDATED%20POM.pdf)
<br>
[Project's Implementation Arrangement](https://doh.gov.ph/sites/default/files/basic-page/DEPARTMENT%20ORDER%20NO.%202021-0205%20IMPLEMENTATION%20ARRANGEMENT.pdf)
<br>
[Guidelines on the Project's Civil Works Implementation](https://doh.gov.ph/sites/default/files/basic-page/dc2020-0398.pdf)
<br>
[Contingency Emergency Response Component -- Emergency Response Operations Manual]()
<br>
[Stakeholder Engagement Plan (SEP) November 22, 2021](https://doh.gov.ph/sites/default/files/basic-page/SEP-nov-22-2021.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) November 22, 2021](https://doh.gov.ph/sites/default/files/basic-page/ESCP-nov-22-2021.pdf)
<br>
[Stakeholder Engagement Plan (SEP) November 03, 2021](https://doh.gov.ph/sites/default/files/basic-page/No%20Watermark_Stakeholder%20Engagement%20Plan%20%28SEP%29_Second%20AF%20PCERP_November%2003%202021.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) November 03, 2021](https://doh.gov.ph/sites/default/files/basic-page/Environmental%20and%20Social%20Commitment%20Plan%20%28ESCP%29_Second%20AF%20PCERP_November%2003%202021_0.pdf)
<br>
[Stakeholder Engagement Plan (SEP) March 23, 2021](https://doh.gov.ph/sites/default/files/basic-page/SEP%2003172021.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) March 23, 2021](https://doh.gov.ph/sites/default/files/basic-page/ESCP%2003172021.pdf)
<br>
[Environmental and Social Management Framework (ESMF) March 23, 2021](https://doh.gov.ph/sites/default/files/basic-page/ESMF%2003172021.pdf)
<br>
[Stakeholder Engagement Plan (SEP) February 4, 2021](https://doh.gov.ph/sites/default/files/basic-page/clean%2002042021%20SEP.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) February 4, 2021](https://doh.gov.ph/sites/default/files/basic-page/02052021%20ESCP%20clean.pdf)
<br>
[Environmental and Social Management Framework (ESMF) February 4, 2021](https://doh.gov.ph/sites/default/files/basic-page/clean%2002042021%20ESMF.pdf)
<br>
[Stakeholder Engagement Plan (SEP) January 8, 2021](https://doh.gov.ph/sites/default/files/basic-page/clean%20rev%2001082021%20SEP-%20vaccine.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) January 8, 2021](https://doh.gov.ph/sites/default/files/basic-page/clean%20rev%2001082021%20ESCP-%20vaccine.pdf)
<br>
[Environmental and Social Management Framework (ESMF) January 8, 2021](https://doh.gov.ph/sites/default/files/basic-page/clean%20rev%2001082021%20ESCP-%20vaccine.pdf)
<br>
[Stakeholder Engagement Plan (SEP) November 25, 2020]()
<br>
[Environmental and Social Commitment Plan (ESCP) November 25, 2020]()
<br>
[Environmental and Social Management Framework (ESMF) November 25, 2020]()
<br>
[Stakeholder Engagement Plan (SEP) October 9, 2020](https://doh.gov.ph/sites/default/files/basic-page/Stakeholder-Engagement-Plan-v20201009.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) October 9, 2020](https://doh.gov.ph/sites/default/files/basic-page/Environmental%20and%20Social%20Commitment%20Plan%20%28ESCP%29%20%281%29.pdf)
<br>
[Environmental and Social Management Framework (ESMF) October 9, 2020](https://doh.gov.ph/sites/default/files/basic-page/ESMF%2011252020%20%281%29.pdf)
<br>
[Stakeholder Engagement Plan (SEP) August 4, 2020](https://doh.gov.ph/sites/default/files/basic-page/Stakeholder%20Engagement%20Plan%20%28SEP%29.pdf)
<br>
[Environmental and Social Commitment Plan (ESCP) August 4, 2020](https://doh.gov.ph/sites/default/files/basic-page/Environmental%20and%20Social%20Commitment%20Plan%20%28ESCP%29.pdf)
<br>
[Environmental and Social Management Framework (ESMF) August 4, 2020](https://doh.gov.ph/sites/default/files/basic-page/Environmental%20and%20Social%20Management%20Framework.pdf)
<br>


# Contact us
For inquiries or recommendations, please fill out the [Public GRM Form](https://ee.kobotoolbox.org/E8S1roA1)
<br><br><br><br>
You may also contact:<br><br>
<b>On the Project:</b><br>
Mr. Manolito A. Novales<br>
Project Coordinator IV / Project Team Leader<br>
[manovales\@doh.gov.ph](mailto:manovales@doh.gov.ph){.email}<br>
(02)8651 7800 local 1317<br>

Mr. Bryan de Guzman <br>
Deputy Project Team Leader for Additional Financing<br>
[jbdeguzman@doh.gov.ph](mailto:jbdeguzman@doh.gov.ph){.email}<br>
(02)8651 7800 local 1317<br>

Ms. Lovelie Q. Zulueta<br>
Deputy Project Team Leader for the Parent Project<br>
[lqzulueta@doh.gov.ph](mailto:lqzulueta@doh.gov.ph){.email}<br>
(02)8651 7800 local 1317<br><br>
<b>On the Environmental and Social Framework:</b>
<br>
Ms. ⁨Maria Krystell G. Banaag-Año⁩
<br>
Environmental and Social Safeguards Specialist<br>
[mkbano\@doh.gov.ph](mailto:mkbano@doh.gov.ph){.email}<br>
(02) 8651 7800 local 2324<br><br>

<b>On the Monitoring and Evaluation:</b><br>
Ms. Vega Fria G. Postrano<br>
Monitoring and Evaluation Specialist<br>
[vfgpostrano\@doh.gov.ph](mailto:vfgpostrano@doh.gov.ph){.email}<br>
(02) 8651 7800 local 1453<br>

Mr. John Conrad P. Dacusin<br>
Project Assistant<br>
[jcpdacusin\@doh.gov.ph](mailto:jcpdacusin@doh.gov.ph){.email}<br>
(02)8651 7800 local 1453<br>

Mr. Mark Benedict K. Mortera<br>
Project Assistant<br>
[mbkmortera\@doh.gov.ph](mailto:mbkmortera@doh.gov.ph){.email}<br>
(02)8651 7800 local 1453<br><br>

<b>On the Deployment of the Project Procured Vaccines</b><br>
Ms. Hannah P. Jara<br>
Vaccine Specialist<br>
hpjara@doh.gov.ph<br>
(02) 8651 7800 local 2361

# Project Dashboards

## Dashboards  {.tabset}

### Form A

<iframe title="PowerBi Form A" width="100%" height="100%" margin="auto" width="100%" src="https://app.powerbi.com/view?r=eyJrIjoiZmVhOTNhMjMtOTEyOS00ZDgwLTgwYTItZTM3MDNmNjZmZjRmIiwidCI6IjE5NWQzN2JlLTllMGEtNDIwNS1hZGY0LWEyNTk5ZTllMWNjYSIsImMiOjEwfQ%3D%3D&pageName=ReportSection" frameborder="0" allowFullScreen="true" data-external="1"></iframe>

### Form B

<iframe title="PowerBi Form B" width="100%" height="100%" margin="auto" src="https://app.powerbi.com/view?r=eyJrIjoiMGE5N2MwNzgtZThkZS00YzA0LWFmZTktZjliZGY3YzdkMTdkIiwidCI6IjE5NWQzN2JlLTllMGEtNDIwNS1hZGY0LWEyNTk5ZTllMWNjYSIsImMiOjEwfQ%3D%3D&pageName=ReportSection" frameborder="0" allowFullScreen="true" data-external="1"></iframe>

### ESMP Community Environmental Health and Safety

<iframe title="ESF 001 ESMP Community Environmental Health and Safety - Total mitigation measures" width="100%" height="100%" margin="auto" src="https://app.powerbi.com/view?r=eyJrIjoiMWYwNzI5ZGUtZDVhZi00MTczLWE1NjEtMTg1ZjMzODUyOTc2IiwidCI6IjE5NWQzN2JlLTllMGEtNDIwNS1hZGY0LWEyNTk5ZTllMWNjYSIsImMiOjEwfQ%3D%3D" frameborder="0" allowFullScreen="true" data-external="1"></iframe>

### ESMP Occupational Health and Safety

<iframe title="ESF 002 ESMP Occupational Health and Safety - Total mitigation measures" width="100%" height="100%" margin="auto" src="https://app.powerbi.com/view?r=eyJrIjoiZmQ2YWJjZDYtYzAzNy00YjVmLWE5M2MtYzA1NjVhZmE4Y2I1IiwidCI6IjE5NWQzN2JlLTllMGEtNDIwNS1hZGY0LWEyNTk5ZTllMWNjYSIsImMiOjEwfQ%3D%3D" frameborder="0" allowFullScreen="true" data-external="1"></iframe>

### PCERP Procured Modern and Pfizer Vaccine Monitoring

<iframe title="PowerBi Moderna_Pfizer_New - Vaccine monitoring" margin="auto" width="100%" height="100%" src="https://app.powerbi.com/view?r=eyJrIjoiNWVkODVkMjMtYTMwYy00ZjlhLWExMTEtZTJjZmI2ZmJjODRkIiwidCI6IjE5NWQzN2JlLTllMGEtNDIwNS1hZGY0LWEyNTk5ZTllMWNjYSIsImMiOjEwfQ%3D%3D" frameborder="0" allowFullScreen="true" data-external="1"></iframe>

