---
title: "PCERP Project Site"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
self_contained: false
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, warning=FALSE}
source("libraries.R")
source("project_recipients.R")
source("project_indicators.R")
source("leaflet_maps.R")
htmltools::tagList(fontawesome::fa_html_dependency())
```


# Project Description

Row
-------------------------------------

### This will be frame 1


### This will be frame 2

```{r}

```


*** 

Some commentary about Frame 2.

### This will be frame 3


### This will be frame 4

Row
----------------------------------------

The Philippines COVID-19 Emergency Response Project (PCERP), with the
Project Development Objective (PDO) to strengthen the Philippines'
capacity to prevent, detect, and respond to the threat posed by COVID-19
and strengthen national systems for public health preparedness, was
approved by the World Bank on 22 April 2020.

Despite recent progress, the Philippines remains one of the countries
most affected by the COVID-19 in East Asia and Pacific, rendering
vaccine purchase and deployment a national priority. With the
availability of vaccines, the Philippines has now an opportunity to add
a significant new layer to its COVID-19 emergency response. Procuring
and administering vaccines is critical to reducing mortality from COVID,
opening the economy in earnest and arresting the decline in GDP,
employment and incomes. Hence, Additional Financing (AF) was sought by
the country to enable affordable and equitable access to COVID-19
vaccines and help ensure effective vaccine deployment in the country
through an enhanced vaccination system and to further strengthen
preparedness and response activities.

The original approved loan financing of US\$ 100 Million (Loan no.
9105-PH) had been increased by US\$ 500 Million through the Additional
Financing in 19 March 2021, to cover the procurement of vaccines against
COVID- 19 and to support the DOH National Deployment and Vaccination
Plan (NDVP) (Loan no. 9220-PH). The new total of the Project financing
is US\$ 600 Million.

The expected project beneficiaries will be the general population,
including infected people, at-risk populations, particularly the elderly
and people with chronic conditions, medical and emergency personnel,
medical and testing facilities, and public health agencies engaged in
the response.

The project is comprised of the following four components:

Component 1: Strengthening Emergency COVID-19 Health Care Response (US\$
577,117,000) with the following sub-component:<br>          1.1
Provision of medical and laboratory equipment and reagents;<br>         
1.2 Provision of medical supplies, including Personal Protective
Equipment (PPE), medical countermeasures, COVID-19 vaccines, medicines,
and ambulances;<br>          1.3 Regular and intensive care isolation
rooms with negative pressure;<br>          1.4 Deployment of COVID-19
vaccines (new sub-component, financed by counterpart funding from the
GOP

Component 2: Strengthening laboratory capacity at national and
sub-national level to support Emerging Infectious Diseases (EIDs)
Prevention, Preparedness, and Response (US\$ 15,678,000): It includes
improving, retrofitting, and refurbishing one national reference
laboratory--the Research Institute for Tropical Medicine (RITM)---as
well as six sub-national and public health laboratories in Baguio, Cebu,
Davao, Surigao City, and Manila;

Component 3: Implementation Management and Monitoring and Evaluation
(US\$ 7,205,000): This component supports project management and
monitoring, including the creation of a project management team and
development of project monitoring and evaluation system; and

Component 4: Contingent Emergency Response Component (CERC) (US\$0),
which supports immediate response to an eligible crisis or health
emergency.

The Project Operations Manual (DOH Department Circular no. 2021-0142),
Project's Implementation Arrangements (DOH Department Order no.
2021-0205), Guidelines on the Project's Civil Works Implementation (DOH
Department Circular no. 2020-0398), and the PCERP Contingency Emergency
Response Component -- Emergency Response Operations Manual [CERC--EROM]
(DOH Department Circular no. 2021-0314) are available in the resources
tab.

The closing date of the Project is on December 29, 2023.

# Project Recipients

## Mapping {.tabset}

### Civil Works

```{r}
plotted_GIS
```
Some commentary about Frame 2.